---
title: "Homework_1"
author: "Student Name"
format: docx
editor: visual
---

This is a template that you will use to submit your weekly homework. It is a Quarto file, which allows you to combine text, code, and results all in the same document. Follow the steps below to see how it works.

## Question 1

Find total opioid deaths in Canada, as well as deaths in each provice.

First, you need to enter the data. You enter the data in a "code chunk", as below. Code chunks are shown in grey highlight in your editor. To insert a code chunk, click the little green button marked "+C" above this text on the top right of this panel (or insert a code chunk using the menu by clicking "Code" and then "Insert code chunk") (or press Alt+Ctrl+I).

A code chunk is a part of the document that will run code in `R`, such as performing calculations and creating figures. You can execute individual lines in the script by puting the cursor on them and pressing ctrl+enter. Try it. It's useful to do this to troubleshoot your script.

```{r}
# Enter province names as a vector.  Note that since province names are characters (not numbers), we put quotes around them.
provs <- c("NL", "PE", "NS", "NB", "QC", "ON", "MB", "SK", "AB", "BC")
# Enter opioid death rates in the same order.  Note that these are numbers, so they don't need any quotes:
death_rates <- c(5.7, 3.5, 6.2, 9.4, 6.2, 16.8, 3.7, 23.9, 33.4, 45.3)
# We can display a vector or variable, just by writing its name:
death_rates
# You also need to enter the population here.  I've started for you, but you need to finish.
pop <- c(510550, 154331)
```

The next step is to put the vectors you created into a data frame. Do that in the code chunk below. We will call the data frame "opiod_data":

```{r}
# fill in the stuff on the right hand side
opioid_data <- data.frame()
```

Finally, you will do the calculations required to find the total number of opiod deaths in each province, as well as the total number of opioid deaths (in 2022) in all of Canada. To do this, create a code chunk below this point and conduct the calculations required.

Once you're done, press the "Render" button in the menu bar above. If all goes well, you should get a Word document with the full answers. At that point, you can modify the text or any of the code in the document as you see fit, and Render it again to update the Word file. You will submit the word document as your homework.

For help with Quarto documents, you can use the Help menu above, and click on "Markdown quick reference".
